Determinism, Complexity, and Predictability in Computer Performance

### 2014-04-22 wpe.tex
fix horrible writing. shouldn't write while tired...

As a final note: there has been prior work under a similar title to
ours~\cite{haven2005}, but there are only superficial similarities
between the two research projects.  Haven \emph{et al.} utilize the
relative entropy to quantify the difference in predictability between
two distributions: one {\color{red}[[Ryan: a distribution ``using'' a
      dynamical system is confusing.  Do you mean ``created using''?
      Or ``measured from''?  And what do you mean by ``from an
      ensemble''?  ensemble of what?  used how?]]}  using the known
dynamical system from a small ensemble in the past, and the other the
asymptotic distribution. Our work quantifies the predictability of a
single observed time series using weighted permutation entropy and
makes no assumptions about the generating process.

>>>>

As a final note: there has been prior work under a similar title to
ours~\cite{haven2005}, but there are only superficial similarities
between the two research projects.  Haven \emph{et al.} utilize the
relative entropy to quantify the difference in predictability between
two distributions: one evolved from a small ensamble of past
states using the known dynamical system, and the other the
asymptotic distribution. Our work quantifies the predictability of a
single observed time series using weighted permutation entropy and
makes no assumptions about the generating process.
